Efficient pedigree recording for fast population genetics simulation

### 2017-12-31 forwards_paper.tex
edit abstract

\begin{abstract}
    In this paper we describe how to
    efficiently record the entire genetic history of a population
    during a forwards-time, individual-based population genetics simulation.
    This allows us to dramatically reduce the computational burden of tracking individual genomes
    by simulating only those loci that may affect reproduction (those having non-neutral variants),
    and recording history in the \emph{tree sequence} format introduced in the software package \msprime,
    on which neutral mutations can be quickly placed afterwards.
    We implement the method in two popular forwards-time simulation frameworks,
    and show that not only does this speed up large simulations by one or two orders of magnitude,
    but saves substantially more information from the simulation
    (all marginal genealogies) than simply recording the final sequences of
    simulated individuals.
    \jda{ this is still only 120 words and we should say 'more than what'}
    % This has the promise of making large-scale, whole-genome simulations with realistic geography and selection finally possible.
\end{abstract}

>>>>

\begin{abstract}
    In this paper we describe how to
    efficiently record the entire genetic history of a population
    during a forwards-time, individual-based population genetics simulation.
    This allows us to dramatically reduce the computational burden of tracking individual genomes
    by simulating only those loci that may affect reproduction (those having non-neutral variants),
    and recording history in the \emph{tree sequence} format introduced in the software package \msprime,
    on which neutral mutations can be quickly placed afterwards.
    We implement the method in two popular forwards-time simulation frameworks,
    and show that not only does this speed up large simulations by one or two orders of magnitude,
    but saves not only full genotype sequences, but also all marginal
    geneologies of the simulated individuals.
    % This has the promise of making large-scale, whole-genome simulations with realistic geography and selection finally possible.
\end{abstract}
